---
title: "Count Missing Values For All Columns By Group"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# countmissing

The goal of countmissing is to, given a data frame `data` and a column `group`, 
  `count_all_missing_by_group()`, create a new data frame with one row per level 
  of `group`. The first column of the output data frame contains the levels of 
  `group`, and the rest of the columns contain the number of missing values for
  all columns in `data` except `group`.

## Installation

You can install the development version of countmissing from [GitHub](https://github.com/) with, insert the following code into your R Console. Make sure to install the countmissing package prior to running count_all_missing_by_group():

``` r

install_github("ahelgason18/countmissing", ref = "0.1.0")

```

## Usage Example

This example demonstrates how to use the count_all_missing_by_group function from the 
  countmissing package to which creates a new data frame with one row per level 
  of `species`. The first column of the output data frame contains the levels of 
  `species`, and the rest of the columns contain the number of missing values for
  each level of `species` for all columns in `penguins` except `species`: 

```{r}
#Load necessary packages for the examples
library(countmissing)
library(dplyr)
library(palmerpenguins)
```

Example 1:
```{r example1}
example1 <- count_all_missing_by_group(penguins, species)
print(example1)
```

Example 2:
```{r example2}

example2 <- penguins |> count_all_missing_by_group(species) 
print(example2)

```


Example 3:
```{r example3}

example3 <- count_all_missing_by_group(penguins, species, .groups = "keep")
print(example3)

```

## License
This package is licensed under the MIT license. 
